Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/methodology.tex
Corrected numbers

The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared. Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless. An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]

@@

@@

In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.  The VUR is defined as the percentage of participants who reported a `5' on the Likert scales. 
We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced. Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 455, ``2'' = 523, ``3'' = 902, ``4''' = 1,746, ``5'' = 6,654). Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.

We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses. Rather, we report medians and quartiles, which are not impacted by outliers. For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%. The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.

>>>>

The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared. There were a total of 288 questions in this set, from which we randomly 6 questions for each participant.

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]

@@

So that we could perform controlled comparisons based on device type, we also included a version of each of these questions in the wearable scenarios section that substituted ``Cubetastic3000'' for ``smartphone.'' Thus, there were a total of 293 Cubetastic3000 scenarios, from which each participant was randomly assigned 6.

@@

In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.  The VUR is defined as the percentage of participants who reported a `5' on the Likert scales. 
We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced. Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344). Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.

We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses. Rather, we report medians and quartiles, which are not impacted by outliers. For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,782 responses, with an initial agreement rate of 89.7\%. The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
